Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Snapshot Reads

\subsection{Snapshot Reads \tbr}
\label{subsec:reads-at-timestamp}

In order to provide snapshot reads, we first need to define
\emph{sufficiently up-to-date}. Therefore Spanner tracks a \emph{safe time},
denoted as $t_{safe}$, at each replica. $t_{safe}$ is defined as the maximum
timestamp at which the corresponding replica is up-to-date. Hence, a replica
satisfies reads at every timestamp $t$ if $t \leq t_{safe}$ holds. Spanner can
then perform a snapshot read at any replica that is sufficiently up-to-date. As
a consequence, snapshot reads have the same performance benefits as provided by
snapshot isolation since they are lock-free.

The safe time is determined by the safe time of a Paxos state machine, denoted
as $t_{safe}^{Paxos}$, and the safe t ime of the transaction manager, i.e.
$t_{safe}^{TM}$. The overall safe time of a replica then is the minimum of
these two. $t_{safe}^{Paxos}$ is simple equal to the time of the highest-applied
Paxos write because if the Paxos level is reached in the spanserver software stack,
then the corresponding transaction has already been committed. $t_{safe}^{TM}$
is $\infty$ if there exist distributed transaction which are in between the two
phases of two phases of the 2-phase commit because in this case the system does
not guaranteed that this transaction will commit.

>>>>

\subsection{Snapshot Reads}
\label{subsec:reads-at-timestamp}

In order to provide snapshot reads, we first need to define
\emph{sufficiently up-to-date}. Therefore Spanner tracks a \emph{safe time},
denoted as $t_{safe}$, at each replica. $t_{safe}$ is defined as the maximum
timestamp at which the corresponding replica is up-to-date. Hence, a replica
satisfies reads at every timestamp $t$ if $t \leq t_{safe}$ holds. Spanner can
then perform a snapshot read at any replica that is sufficiently up-to-date. As
a consequence, snapshot reads have the same performance benefits as provided by
snapshot isolation since they are totally lock-free.

The safe time is determined by the safe time of a Paxos state machine, denoted
as $t_{safe}^{Paxos}$, and the safe time of the transaction manager, i.e.
$t_{safe}^{TM}$. The overall safe time of a replica then is the minimum of
these two.

$t_{safe}^{Paxos}$ is simply assigned the time of the highest-applied Paxos write
because if the Paxos level is reached in the spanserver software stack, then the
corresponding transaction has already been committed. $t_{safe}^{TM}$ is $\infty$
if there exists a distributed transaction which is in between the two phases of
the two-phase commit because in this case the system does not know if this
transaction will commit.
